Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-08 paper.tex
Modified related work

\emph{Flow analysis} is a topic of theoretical interest and practical importance in various disciplines. 
Flow analysis is conventionally conducted to study spatial dynamics and identify routine patterns in the movement of people.
For instance, interest in modelling traffic flows emerged from the strain placed on urban transportation systems during peak hours~\cite{roth,ferreira}.
Likewise, insight into routine travel patterns is crucial for the conceptualization of functional urban areas~\cite{servillo2013town}, urban hierarchies~\cite{christaller1966central} and other territorial structures.

@@

A number of solutions have been proposed for clutter reduction. 
Filtering is the most commonly practiced. 
The same goal can be achieved by clustering lines that have similar properties like common start, end or intermediate locations \cite{andrienko2007visual} . 
Both solutions are effective at reducing clutter yet it should be noted that excessive aggregation or filtering removes a significant amount of information from the visualization.
Another solution is to transform the visual representation. 
Flow maps \cite{phan2005flow} reduces clutter by rerouting the arrows to minimize intersection and obtain layouts that align with key geographic features like roads, rivers or coastlines. 
However, a certain degree of ambiguity is introduced to the visualization since the arrows do not depict actual paths of movement and maybe misleading to interpret.

>>>>

\emph{Flow analysis} is a topic of theoretical interest and practical importance conventionally conducted to study spatial dynamics and identify routine patterns in the movement of people.
For instance, interest in modelling traffic flows emerged from the strain placed on urban transportation systems during peak hours~\cite{roth,ferreira}.
Likewise, insight into routine travel patterns is crucial for the conceptualization of functional urban areas~\cite{servillo2013town}, urban hierarchies~\cite{christaller1966central} and other territorial structures.

@@

A number of solutions have been proposed for clutter reduction. 
Filtering is the most commonly practiced. 
The same goal can be achieved by clustering lines that have similar properties like common start, end or intermediate locations \cite{andrienko2007visual}. 
Both solutions are effective at reducing clutter yet it should be noted that excessive aggregation or filtering removes a significant amount of information from the visualization.

Another solution is to transform the visual representation. 
Flow maps \cite{phan2005flow} reduces clutter by rerouting the arrows to minimize intersection and obtain layouts that align with key geographic features like roads, rivers or coastlines. 
However, a certain degree of ambiguity is introduced to the visualization since the arrows do not depict actual paths of movement and maybe misleading to interpret.
A computationally cost effective alternative is to draw links as arcs instead of arrows \cite{chua2014flowsampler}.
Yet, this visual encoding may intensify the visual complexity of the representation.
